INTELLIGENT SYSTEMS

### 2021-04-14 papers/paper_7.tex
finish 7.4.1

>>>>

\subsubsection{Gaussian Noise Plus Impulse Noise}
The overall noise can consist of several noise distributions. Previously, the 
operations useful for obtaining information on a Gaussian noise distribution 
have been defined. When the Gaussian distribution assumes random values 
(called salt and pepper), and therefore not uniformly distributed, then the 
optimization problem becomes more difficult. In order to find a solution, it 
is necessary to approximate a part of the PDF concerning the random-value 
noise by a Gaussian function, which means that it is possible to use the 
Gaussian mixture noise model to optimize the Gaussian plus impulse noise.

\subsection{EXPERIMENTAL RESULTS}
The experiments are conducted on mixed-noise Gaussian noise and on Gaussian 
plus impulse noise. The indices used to estimate the quality of the restructured
images are the \emph{Signal-to-Noise Ratio} (PSNR) and the \emph{Structural 
Similarity Index} (SSIM) \cite{0884882841}.

\subsubsection{Gaussian Mixed Noise}
The quality comparison is done with different methods already existing in 
the state of the art. From figure \ref{fig:GMNComp} you can see the application of 
each of these methods on an image in which there is the presence of mixed-noise. 
The proposed method produces a restructured image with a better level of 
texture detail.
\begin{figure}[h!]
    \centering
    \includegraphics[width = \linewidth]{images/paper7/GMN comparison.png}
    \centering
    \caption{Image reconstruction under Gaussain mixture noise comparison.}
    \label{fig:GMNComp}
\end{figure}

To test the efficiency of the methods, several images belonging to a 
BSD100 dataset \cite{0884882842} were taken on which there are two Gaussian noises ($n_1$ 
and $n_2$) with different mixture $r_1, r_2$ and standard deviation ($\sigma$). By comparing the 
results obtained in table \ref{indexCompare}, the proposed method achieves the highest values 
in both indices compared to the two methods \cite{0884882815} \cite{0884882819} most common in the 
state of the art.
\begin{table}[h!]
    \centering
    \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|c||ccc|ccc|ccc|}
        \hline
            & \multicolumn{3}{c||}{$\sigma_1=5 ~~~\sigma_2=30 $} & \multicolumn{3}{c||}{$\sigma_1=10 ~~~\sigma_2=50 $} & \multicolumn{3}{c||}{$\sigma_1=15 ~~~\sigma_2=75 $}\\
        \hline        
        $r_1:r_2\rightarrow$ & 0.3:0.7 & 0.5:0.5 & 0.7:0.3 & 0.3:0.7 & 0.5:0.5 & 0.7:0.3 & 0.3:0.7 & 0.5:0.5 & 0.7:0.3\\
        \hline 
        \hline
        \multirow{2}{*}{PGPD\cite{0884882815}} & 29.42 & 30.16 & 31.19 & 27.23 & 27.88 & 28.78 &25.64 & 26.26 & 27.14\\
        & 0.8132 & 0.8349 & 0.8544 & 0.7404 & 0.7634 & 0.7874 & 0.6790 & 0.7044 & 0.7336\\
        \hline
        \multirow{2}{*}{IRCNN\cite{0884882819}} & 29.83 & 30.53 & 31.48 & 27.66 & 28.25 & 29.04 & 19.37 & 25.22 & 27.32\\
        & 0.8262 & 0.8451 & 0.8664 & 0.7611 & 0.7789 & 0.7993 & 0.2948 & 0.6423 & 0.7426\\
        \hline
        \multirow{2}{*}{Proposed} & \bfseries{29.88} & \bfseries{31.26} & \bfseries{32.72} & \bfseries{28.01} & \bfseries{29.00} & \bfseries{30.37} & \bfseries{26.23} & \bfseries{27.41} & \bfseries{28.84}\\
        & \bfseries{0.8273} & \bfseries{0.8785} & \bfseries{0.9094} & \bfseries{0.7801} & \bfseries{0.8112} & \bfseries{0.8528} & \bfseries{0.6931} & \bfseries{0.7613} & \bfseries{0.8077}\\
        \hline
    \end{tabular}
    \end{adjustbox}
    \caption{Average PSNR and SSIM values on BSD100 datasets of some methods.}
    \label{indexCompare}
\end{table}
